BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Control Flow Analysis for Realistic BPMN Models

### 2024-07-05 main.tex
Check

\textbf{Second}, we benchmarked the tool against a synthetic data set of models that lead to a state space explosion.
This represents a \textit{worst case} scenario for formal analysis.
We generated a data set of models~\cite{krauterInstantaneousComprehensibleFixable2024} with a growing number of parallel branches with increasing length, similar to~\cite{corradiniFormalApproachAnalysis2021}.
\autoref{tab:parallel-branches-benchmark} shows the average runtime of our tool when analyzing these models.
The BPMN Analyzer explores the entire state space while simultaneously analyzing the control flow, i.e., verifying soundness properties.

@@

% They also want this section
\section{Maturity of the tool} \label{sec:maturity}
The BPMN Analyzer is our newest tool, incorporating many findings from our previous work~\cite{krauterFormalizationAnalysisBPMN2023} while focusing on instantaneous and understandable error detection.
The tool is open-source~\cite{krauterInstantaneousComprehensibleFixable2024}, and we aim to achieve high code quality by employing industry best practices such as rigorous static analysis, testing, and consistent formatting.
Furthermore, we demonstrated the tool to companies in the BPMN process orchestration space and received positive initial feedback, as described in the introduction.

% Scalability tests (instantaneous) --> Generated models are public, including our tool for future direct comparisons
As described in the previous section, we benchmarked our tool runtime in three scenarios.
The tool can check most models instantaneously, and we provide more details, including scripts and data needed to reproduce our results in~\cite{krauterInstantaneousComprehensibleFixable2024}.

>>>>

\textbf{Second}, we benchmarked the tool against a synthetic data set of models that lead to a state space explosion.
This represents a \textit{worst case} scenario for formal analysis.
We generated a data set of models~\cite{krauterInstantaneousComprehensibleFixable2024} with a growing number of parallel branches with increasing length as shown in \autoref{fig:parallel-branches-models}, similar to~\cite{corradiniFormalApproachAnalysis2021}.

\begin{figure}[ht]
	\centering
	\includegraphics[width=1\linewidth]{images/parallel-branches}
	\caption{Models with a growing number of parallel branches and branch length}
	\label{fig:parallel-branches-models}
\end{figure}

\autoref{tab:parallel-branches-benchmark} shows the average runtime of our tool when analyzing these models.
The BPMN Analyzer explores the entire state space while simultaneously analyzing the control flow, i.e., verifying soundness properties.

@@

\section{Maturity of the tool} \label{sec:maturity}
The BPMN Analyzer is our newest tool, incorporating many findings from our previous work~\cite{krauterFormalizationAnalysisBPMN2023} while focusing on instantaneous and understandable error detection.
The tool is open-source~\cite{krauterInstantaneousComprehensibleFixable2024}, and we aimed for high code quality by employing industry best practices such as rigorous static analysis, testing, and consistent formatting.
Furthermore, we demonstrated the tool to companies in the BPMN process orchestration space and received positive feedback~\cite{krauterInstantaneousComprehensibleFixable2024}.

As described in the previous section, we benchmarked our tool runtime in three scenarios.
The tool can check most models instantaneously, and we provide more details, including scripts and all models needed to reproduce our results in~\cite{krauterInstantaneousComprehensibleFixable2024}.
